Lobbying and Legislative Uncertainty

### 2016-04-15 presentation.tex
finish model section and conclusions

\begin{frame}{D}
\pause
  Objective function:
\pause
\[
  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
\vskip-.1in
\pause
\begin{itemize}[<+->]
	\item S
		\begin{itemize}
			\item $s$: 
			\item $e$: 
		\end{itemize}
	\item Optimal 
		\begin{itemize}
			\item Ignores 
			\item Takes 
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{D}
\pause
  Objective function:
\pause
\[
  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
\vskip-.1in
\pause
\begin{itemize}[<+->]
	\item S
		\begin{itemize}
			\item $s$: 
			\item $e$: 
		\end{itemize}
	\item Optimal 
		\begin{itemize}
			\item Ignores 
			\item Takes 
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Political Pressure}
Two potential sources
\pause
\begin{enumerate}[<+->]
	\item Endogenous effort choice of lobby, $e$
		\begin{itemize}[<+->]
			\item Lobby chooses effort to maximize profits, $\pi(\cdot)$, net of lobbying effort, $e$
			\item Call lobby's optimal effort choice $e^L$
						\[
						  e^L = \max_e \pi(\tau(\ga(e))) - e
						\]
		\end{itemize}
\end{enumerate}

@@

@@

\begin{frame}{Future Work}
\pause
\begin{itemize}[<+->]
	\item A
	\item I
	\item C
\end{itemize}

@@

\begin{frame}{Conclusion}
Taking into account
\pause
\begin{itemize}[<+->]
		\item provides 
		\item demonstrates 
		\item helps 
\end{itemize}

>>>>

\begin{frame}{Legislators}
\pause
Take ideal point to be linear: $\alpha - \beta i$
\pause
\begin{itemize}[<+->]
	\item Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
		\begin{itemize}
			\item Probability $i$ votes for $s$ is $\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right] = \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right] $
			\item Assuming $\ta \sim \text{Logistic} \ (0,1)$, it's $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
		\end{itemize}
\end{itemize}

@@

\begin{frame}{Vote Buyer B}
\pause
Assume vote buyers maximize expected value of winning net of bribes paid  
\begin{itemize}[<+->]
	\item Assume bribes must be non-negative
	\item Vote buyer won't spend more than his willingness to pay, $W_B$
	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
\end{itemize}
\end{frame}

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $X(i) = 1$ denote legislator $i$ votes for the status quo
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
\end{itemize}
\end{frame}

@@

\begin{frame}{Next Steps}
\pause
\begin{itemize}[<+->]
	\item Modify model so that both legislators can lobby the \textit{same} legislator in equilibrium
	\item Derive tight identification of empirical estimates from structural model
	\item Provide micro-founded explanations for the variation in uncertainty that lobbies face
\end{itemize}

@@

\begin{frame}{Conclusion}
Taking into account uncertainty about the preferences of legislators brings vote buying models closer to capturing important stylized facts
\pause
\begin{itemize}[<+->]
		\item helps in understanding lobbying strategies
		\item may shed light on why some lobbies are more successful than others
		\item will help in the identification of measures of uncertainty that can be used in many applications
\end{itemize}
